---
output: html_document
---

## Excercise 8.8

__In the lab, a classification tree was applied to the Carseats data set after converting Sales into a qualitative response variable. Now we will seek to predict Sales using regression trees and related approaches, treating the response as a quantitative variable.__

a. __Split the data set into a training set and a test set.__

```{r}
library(ISLR)
set.seed(1)
train <- sample(1:nrow(Carseats), nrow(Carseats) / 2)
Carseats.train <- Carseats[train, ]
Carseats.test <- Carseats[-train, ]
```


b. __Fit a regression tree to the training set. Plot the tree, and interpret the results. What test MSE do you obtain?__

```{r}
library(tree)
tree.carseats <- tree(Sales ~ ., data = Carseats.train)
summary(tree.carseats)

plot(tree.carseats)
text(tree.carseats, pretty = 0)

yhat <- predict(tree.carseats, newdata = Carseats.test)
mean((yhat - Carseats.test$Sales)^2)
```
~ 4.15

c. __Use cross-validation in order to determine the optimal level of tree complexity. Does pruning the tree improve the test MSE?__

```{r}
cv.carseats <- cv.tree(tree.carseats)
plot(cv.carseats$size, cv.carseats$dev, type = "b")
tree.min <- which.min(cv.carseats$dev)
points(tree.min, cv.carseats$dev[tree.min], col = "red", cex = 2, pch = 20)
```
```{r}
prune.carseats <- prune.tree(tree.carseats, best = 8)
plot(prune.carseats)
text(prune.carseats, pretty = 0)

```
```{r}
yhat <- predict(prune.carseats, newdata = Carseats.test)
mean((yhat - Carseats.test$Sales)^2)
```
The test improves to 5.1

d. __Use the bagging approach in order to analyze this data. What test MSE do you obtain? Use the `importance()` function to determine which variables are most important.__

```{r}
library(randomForest)
set.seed(1)
bag.carseats = randomForest(Sales~.,data=Carseats,mtry=10,subset=train,importance=T)
bag.carseats
yhat.bag = predict(bag.carseats,newdata=Carseats[-train,])
importance(bag.carseats)
varImpPlot(bag.carseats)
```
```{r}
importance(bag.carseats)
```


e. __Use random forests to analyze this data. What test MSE do you obtain? Use the `importance()` function to determine which variables are most important. Describe the effect of m, the number of variables considered at each split, on the error rate obtained__

```{r}
rf.carseats <- randomForest(Sales ~ ., data = Carseats.train, mtry = 3, ntree = 500, importance = TRUE)
yhat.rf <- predict(rf.carseats, newdata = Carseats.test)
mean((yhat.rf - Carseats.test$Sales)^2)
```
```{r}
importance(rf.carseats)
```
The more important variables consist of "Price" and "ShelveLoc"
